\LARGE \bf Human-Robot Interaction: Tackling the AI Challenges

### 2014-05-05 paper.tex
Completed discussion on memory
Closes #20

\subsubsection{Working memory}

The {\sc Oro} server also features a mechanism to mimic minimalistic forms of
memory families.  When new statements are inserted in the knowledge base, a
\emph{memory profile} is optionally attached to them.

Three such profiles are predefined: {\tt short term}, {\tt episodic} and {\tt
long term}. They are currently attached to different lifetime for the statements
(respectively 10 seconds, 5 minutes and no time limit). After this duration,
the statements are automatically removed from the knowledge base.

@@

>>>>

\subsubsection{Working memory}
\label{memory}

Memory has been studied at length in the cognitive psychology and
neuropsychology communities: very briefly, the idea of \emph{short-term} and
\emph{long-term} memory is due to Atkinson and Shiffrin~\cite{Atkinson1968} ,
Anderson~\cite{Anderson1976} splits memory into \emph{declarative} (explicit)
and \emph{procedural} (implicit) memories, Tulving~\cite{Tulving1985} organises
the concepts of \emph{procedural}, \emph{semantic} and \emph{episodic} memories
into a hierarchy. Short-term memory is eventually refined with the concept of
\emph{working memory} by Baddeley~\cite{Baddeley2010}

It is worth emphasising that if memory is commonly associated to the process of
forgetting facts after a variable amount of \emph{time}, it actually covers
more mechanisms that are relevant to robotics, like selective remembering
triggered by a specific context or reinforcement learning.

The {\sc Oro} server features a mechanism to mimic only minimalistic forms of memory
families.  When new statements are inserted in the knowledge base, a
\emph{memory profile} is optionally attached to them.  Three such profiles are
predefined: {\tt short term}, {\tt episodic} and {\tt long term}. They are
currently attached to different lifetime for the statements (respectively 10
seconds, 5 minutes and no time limit). After this duration, the statements are
automatically removed from the knowledge base.

@@

In the larger field of cognitive architectures, the {\sc Soar}
architecture~\cite{Lehman2006} is one of those that tries to reproduce a
human-like memory organisation. The GLAIR cognitive
architecture~\cite{Shapiro2009} also has a concept of long term/short term and
episodic/semantic memories.
